Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Remove comment
Simplify Implementation -> Haddock

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}

\begin{quote}
TBD:
\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.

    \emph{kazu: I guess that it's enough to describe this in the Implementation Section.}
\end{itemize}
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Haddock}
\label{sec:haddock}

Haddock before version 2.8 had markup syntax for
code blocks, but not for evidence.
We implemented support for interactive examples ({\tt >>>}) in
Haddock 2.8.
We also added support for markup of properties ({\tt prop>}) which
will be available in a future release.
Both interactive examples and properties in Haddock comments are
included in the generated documentation.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Haddock}
\label{sec:haddock}

We added markup support for interactive examples to Haddock, and it is
available since version 2.8.
We also added markup support for properties, which will be included in
a future release of Haddock.
